Scalable and Parameter-Free Exploration in Deep Reinforcement Learning

### 2022-01-10 papers/main.tex
TEMPORARY DEPLOY COMMIT

\subsection{Functional Variational Bayesian Neural Networks}
There are several ways of approximating the posterior distribution of the weights
in a neural network with respect to a prior and a dataset. Typically, a static dataset
\(\D\)
Functional variational Bayesian neural networks \citep{sun_functional_2019} is 
a variational inference method for neural networks that approximates the 
posterior distribution in function space.
\citet{sun_functional_2019} show that for two stochastic processes \(P\) and \(Q\):

>>>>

\subsection{Functional Variational Bayesian Neural Networks}
There are several ways of approximating the posterior distribution of the weights
in a neural network with respect to a prior and a dataset. Typically, the dataset
\(\D\) is static and with datapoints \(\bm{x}\) and labels \(\bm{y}\), and the 
prior is defined as a distribution over the weights
\(p(\bm{w})\)~\citep{rezende_stochastic_2014,blundell_weight_2015,ritter_scalable_2018,maddox_simple_2019}.

Functional variational Bayesian neural networks \citep{sun_functional_2019} is 
a variational inference method for neural networks that approximates the 
posterior distribution in function space.
\citet{sun_functional_2019} show that for two stochastic processes \(P\) and \(Q\):
